Evaluation of Types

### 2020-05-15 evaluation/R/evaluate-type-analysis.Rmd

>>>>

##

```{r, eval = TRUE, verbose = FALSE}
function_polymorphic_freq <-
union_data %>%
distinct(package_name, function_name, parameter_position) %>%
mutate(polymorphic = ifelse(alternative_count > 1, true, is_polymorphic(alternative_count)) %>%
group_by(package_name, function_name) %>%
summarize(polymorphic_position_count = sum(polymorphic)) %>%
ungroup() %>%
group_by(polymorphic_position_count) %>%
summarize(function_count = ()) %>%
ungroup() %>%
arrange(polymorphic_position_count)

function_polymorphic_freq %>%
ggplot(aes(polymorphic_position_count, function_count)) +

```
